\documentclass[12pt,letterpaper]{article}
\usepackage{fullpage}
\usepackage[top=2cm, bottom=4.5cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage{amsmath,amsthm,amsfonts,amssymb,amscd}
\usepackage{lastpage}
\usepackage{enumerate}
\usepackage{fancyhdr}
\usepackage{mathrsfs}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{hyperref}

\hypersetup{%
  colorlinks=true,
  linkcolor=blue,
  linkbordercolor={0 0 1}
}
 
\setlength{\parskip}{0.05in}

% Edit these as appropriate
\newcommand\course{CS 6620}
\newcommand\hwnumber{4}                  % <-- homework number

\pagestyle{fancyplain}
\headheight 35pt
\lhead{14 points}
\chead{\textbf{\Large Homework \hwnumber}}
\rhead{\course \\ assigned: 10/21/2019\\ 
oral due: 11/20 - 12/04, 2019\\
written due: 12/04/2019
}
\lfoot{}
\cfoot{}
\rfoot{}
\headsep 1.5em

\begin{document}
~

You are to select, study, and present a compiler-related ``topic'' to the class.
The papers listed on the web-site are all possible topics for you to
choose from, but if you have another idea please contact me to discuss it.
For your chosen topic you are expected to:
\begin{itemize}
\item Explain the topic does both conceptually and through examples;
\item Relate the topic to the concepts, data structures and algorithms studies in the class; and
\item Illustrate the topic in action on a realistic program fragment.
\end{itemize}
This assignment must be completed working with a partner.  Unlike the
other homeworks, on this one you can team up with a partner from a 
prior homework. 

The first thing you should do on this assignment is to sign up for
a 25 minute presentation slot on Nov. 18, Nov. 20, Nov. 25, and Dec. 02.  
You can sign up by sending the instructor an email with the names
of the team members and the topic you choose.
There are 3 slots per class and they will be assigned on a first-come 
first-served basis.  When presenters sign-up I will update the 
course web-page.

\section*{Part 1 (4 points)}
Prepare a detailed outline of the material that you plan to present
to the class related to your topic.  This should take 1-2 pages and
describe how you will motivate the topic and put it into the context
of the class, the examples you plan to use to illustrate the topic,
and the technical material that you plan to present.
You should take into account that you will only have 25 minutes, so
the challenge here is in distilling the material down to its essence
so that you can clearly communicate it to the class.

This outline is due 9 days before your scheduled presentation.
It can be sent to the instructor via email and you will receive
feedback 7 days before your scheduled presentation so that you
have time to incorporate the feedback.

\section*{Part 2 (10 points)}
Prepare and deliver a 25 minute presentation on your
selected pass.  You should cover all of the areas discussed above with
the goal of providing a ``tutorial'' introduction to your topic.

Both team members are required to participate in the presentation.
You will be graded on the organization of your presentation,
the quality of your presentation materials,
the clarity of your explanations,
the extent to which you use your 25 minutes appropriately (i.e., being
on time),
and your ability to answer questions during your presentation. 

There are many good resources available online about how to prepare
and give a technical presentation.  This site is a nice example:
\url{https://homes.cs.washington.edu/~mernst/advice/giving-talk.html}

You may use any slide preparation system you would like, but you 
will submit a PDF copy of the slides or lecture notes you use 
in making your presentation.

\end{document}


